Title

### 2024-05-31 paper/main.tex
Updates format

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2024

% ready for submission
\usepackage{neurips_2024}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2024}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2024}

% to avoid loading the natbib package, add option nonatbib:
%    \usepackage[nonatbib]{neurips_2024}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors

% Packages added by me.
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{bm}
\usepackage{subcaption}
\usepackage[ruled]{algorithm2e}

@@

\title{Title}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
  David S.~Hippocampus\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

To perform any causal effect identification or estimation using Directed
Acyclic Graphs (DAGs) or Structural Equation Models (SEMs), researchers need to
first construct a causal structure. This process of constructing the casual
structure from data is known as \emph{Causal Discovery}. In the field of DAGs,
plenty of algorithms have been developed to automatically construct DAGs from
data. These algorithm takes different approaches to causal discovery such as
Constraint-based algorithms such as PC and Fast Causal Infenrece (FCI) where
the algorithm tries to match the conditional independences in the data to the
ones impled by the model, score-based methods such as Hill-Climb Search, Greedy
Equivalence Search (GES)  where the algorithm tries to find a model that has
the best score given some scoring metric, and continuous optimization where the
problem is formulated as a constrained optimization problem such as No Tears.

@@

\begin{figure}
		\centering
		\begin{tikzpicture}
			\begin{scope}[yshift=0.7cm, scale=1]
			\tikzstyle{every node}=[align=center, inner sep=1pt]
				\node (sex) at (-0.7, -0.8) {Sex};
				\node (age) at (-0.3, 0) {Age};
				\node (ed) at (-1.8, -1.6) {Education};
				\node (occ) at (1.8, 0) {Occupation};
				\node (hrpw) at (1.3, -1.6) {Hours Per \\ Week};
				\node (income) at (-0.7, -2.8) {Income};

				\draw[->]  (age) to[bend right=20] (ed);
				\draw[->]  (sex) to (ed);
				\draw[->]  (age) to (hrpw);
				\draw[->]  (ed) to (hrpw);
				\draw[->]  (sex) to (hrpw);
				\draw[->]  (ed) to (income);
				\draw[->]  (hrpw) to (income);
				\draw[->]  (occ) to[out=300, in=0, looseness=1.4] (income.east);
				\draw[->]  (sex) to (income);
				\draw[->]  (ed) to[out=90, in=150, looseness=1.3] (occ);
				\draw[->]  (sex) to (occ);	
			\end{scope}
			\draw[thick, ->, double, cyan] (2.5,0) -- (3,0);
			\node[rectangle, align=center, inner sep=1pt] at (6, 0) {
				\begin{minipage}{\textwidth}
					\begin{equation*}
						\begin{split}
							\textnormal{Age} &\ci \textnormal{Incm} \rvert \textnormal{Edct, Hrpw, Sex} \\
							\textnormal{Age} &\ci \textnormal{Occp} \rvert \textnormal{Edct, Sex} \\
							\textnormal{Age} &\ci \textnormal{Sex} \\
							\textnormal{Hrpw} &\ci \textnormal{Occp} \rvert \textnormal{Edct, Sex} \\
						\end{split}
					\end{equation*}
				\end{minipage}
				};
		\end{tikzpicture}
		\caption{\todo[inline]{Show a full example of testing using this model}}
\end{figure}

@@

\begin{algorithm}
	\caption{Expert Simulation}
	\While{True}{
	   $ e \gets \textnormal{Effects}(G) > \textnormal{THRESHOLD} $\;
	   $ e \gets e - \textnormal{blacklist} $\;
	   \If {$ e = 0 $}{
		$ G \gets G - e $ \;
		$ \textnormal{blacklist} \gets \textnormal{blacklist} \cup e $\;
	   } \;
	   \If{$ \textnormal{len}(e) = 0$}{
		   $ \textnormal{return}(G) $\;
	   }
	   $ X, Y \gets \max_{X, Y} e $\;
	   $ dir \gets Expert(X, Y, \alpha) $\;
	   $ G \gets G \cup dir $\;
	}

\end{algorithm}

@@

\subsection{Results}
\begin{figure}
	\begin{subfigure}{0.5\textwidth}
		\includegraphics{../code/plots/shd_ribbon.pdf}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\includegraphics{../code/plots/sid_ribbon.pdf}
	\end{subfigure}
\end{figure}

@@

\bibliographystyle{plain}
\bibliography{references.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Appendix / supplemental material}

Optionally include supplemental material (complete proofs, additional experiments and plots) in appendix.
All such materials \textbf{SHOULD be included in the main submission.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\include{checklist}

\end{document}

>>>>

%File: anonymous-submission-latex-2024.tex
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage[submission]{aaai24}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS
%
% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
\usepackage{algorithm}
\usepackage{algorithmic}

%
% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
\usepackage{newfloat}
\usepackage{listings}
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
\lstset{%
	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
\floatstyle{ruled}
\newfloat{listing}{tb}{lst}{}
\floatname{listing}{Listing}
%
% Keep the \pdfinfo as shown here. There's no need
% for you to add the /Title and /Author tags.
\pdfinfo{
/TemplateVersion (2024.1)
}

% DISALLOWED PACKAGES
% \usepackage{authblk} -- This package is specifically forbidden
% \usepackage{balance} -- This package is specifically forbidden
% \usepackage{color (if used in text)
% \usepackage{CJK} -- This package is specifically forbidden
% \usepackage{float} -- This package is specifically forbidden
% \usepackage{flushend} -- This package is specifically forbidden
% \usepackage{fontenc} -- This package is specifically forbidden
% \usepackage{fullpage} -- This package is specifically forbidden
% \usepackage{geometry} -- This package is specifically forbidden
% \usepackage{grffile} -- This package is specifically forbidden
% \usepackage{hyperref} -- This package is specifically forbidden
% \usepackage{navigator} -- This package is specifically forbidden
% (or any other package that embeds links such as navigator or hyperref)
% \indentfirst} -- This package is specifically forbidden
% \layout} -- This package is specifically forbidden
% \multicol} -- This package is specifically forbidden
% \nameref} -- This package is specifically forbidden
% \usepackage{savetrees} -- This package is specifically forbidden
% \usepackage{setspace} -- This package is specifically forbidden
% \usepackage{stfloats} -- This package is specifically forbidden
% \usepackage{tabu} -- This package is specifically forbidden
% \usepackage{titlesec} -- This package is specifically forbidden
% \usepackage{tocbibind} -- This package is specifically forbidden
% \usepackage{ulem} -- This package is specifically forbidden
% \usepackage{wrapfig} -- This package is specifically forbidden
% DISALLOWED COMMANDS
% \nocopyright -- Your paper will not be published if you use this command
% \addtolength -- This command may not be used
% \balance -- This command may not be used
% \baselinestretch -- Your paper will not be published if you use this command
% \clearpage -- No page breaks of any kind may be used for the final version of your paper
% \columnsep -- This command may not be used
% \newpage -- No page breaks of any kind may be used for the final version of your paper
% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
% \pagestyle -- This command may not be used
% \tiny -- This is not an acceptable font size.
% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference

\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{bm}
\usepackage{subcaption}
% \usepackage[ruled]{algorithm2e}

@@

% The file aaai24.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%

% Title

% Your title must be in mixed case, not sentence case.
% That means all verbs (including short verbs like be, is, using,and go),
% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
% articles, conjunctions, and prepositions are lower case unless they
% directly follow a colon or long dash
\title{Title}
\author{
    %Authors
    % All authors must be in the same font size and format.
    Written by AAAI Press Staff\textsuperscript{\rm 1}\thanks{With help from the AAAI Publications Committee.}\\
    AAAI Style Contributions by Pater Patel Schneider,
    Sunil Issar,\\
    J. Scott Penberthy,
    George Ferguson,
    Hans Guesgen,
    Francisco Cruz\equalcontrib,
    Marc Pujol-Gonzalez\equalcontrib
}
\affiliations{
    %Afiliations
    \textsuperscript{\rm 1}Association for the Advancement of Artificial Intelligence\\
    % If you have multiple authors and multiple affiliations
    % use superscripts in text and roman font to identify them.
    % For example,

    % Sunil Issar\textsuperscript{\rm 2},
    % J. Scott Penberthy\textsuperscript{\rm 3},
    % George Ferguson\textsuperscript{\rm 4},
    % Hans Guesgen\textsuperscript{\rm 5}
    % Note that the comma should be placed after the superscript

    1900 Embarcadero Road, Suite 101\\
    Palo Alto, California 94303-3310 USA\\
    % email address must be in roman text type, not monospace or sans serif
    proceedings-questions@aaai.org
%
% See more examples next
}

%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
\iffalse
\title{My Publication Title --- Single Author}
\author {
    Author Name
}
\affiliations{
    Affiliation\\
    Affiliation Line 2\\
    name@example.com
}
\fi

\iffalse
%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
\title{My Publication Title --- Multiple Authors}
\author {
    % Authors
    First Author Name\textsuperscript{\rm 1},
    Second Author Name\textsuperscript{\rm 2},
    Third Author Name\textsuperscript{\rm 1}
}
\affiliations {
    % Affiliations
    \textsuperscript{\rm 1}Affiliation 1\\
    \textsuperscript{\rm 2}Affiliation 2\\
    firstAuthor@affiliation1.com, secondAuthor@affilation2.com, thirdAuthor@affiliation1.com
}
\fi

@@

\emph{Causal discovery} is the process of identifying and understanding causal
relationships among variables in a dataset.

To perform any causal effect identification or estimation using Directed
Acyclic Graphs (DAGs) or Structural Equation Models (SEMs), researchers need to
first construct a causal structure. This process of constructing the casual
structure from data is known as \emph{causal discovery}. In the field of DAGs,
a lot of effort has been put on developing automated algorithms that can
construct these DAGs from data. These algorithm takes different approaches to
causal discovery such as Constraint-based algorithms such as PC and Fast Causal
Infenrece (FCI) where the algorithm tries to match the conditional
independences in the data to the ones impled by the model, score-based methods
such as Hill-Climb Search, Greedy Equivalence Search (GES)  where the algorithm
tries to find a model that has the best score given some scoring metric, and
continuous optimization where the problem is formulated as a constrained
optimization problem such as No Tears.

@@

\begin{figure}
		\centering
		\begin{tikzpicture}
			\begin{scope}[xshift=-2.5cm, yshift=0.7cm, scale=0.7]
			\tikzstyle{every node}=[align=center, inner sep=1pt]
				\node (sex) at (-0.7, -0.8) {Sex};
				\node (age) at (-0.3, 0) {Age};
				\node (ed) at (-1.8, -1.6) {Education};
				\node (occ) at (1.8, 0) {Occupation};
				\node (hrpw) at (1.3, -1.6) {Hours Per \\ Week};
				\node (income) at (-0.7, -2.8) {Income};

				\draw[->]  (age) to[bend right=20] (ed);
				\draw[->]  (sex) to (ed);
				\draw[->]  (age) to (hrpw);
				\draw[->]  (ed) to (hrpw);
				\draw[->]  (sex) to (hrpw);
				\draw[->]  (ed) to (income);
				\draw[->]  (hrpw) to (income);
				\draw[->]  (occ) to[out=300, in=0, looseness=1.4] (income.east);
				\draw[->]  (sex) to (income);
				\draw[->]  (ed) to[out=90, in=150, looseness=1.3] (occ);
				\draw[->]  (sex) to (occ);	
			\end{scope}
			\begin{scope}[xshift=-3cm]
				\draw[thick, ->, double, cyan] (2.5,0) -- (3,0);
				\node[rectangle, align=center, inner sep=1pt] at (5, 0) {
					\begin{minipage}{.2\textwidth}
						\begin{equation*}
							\begin{split}
								\textnormal{Age} &\ci \textnormal{Incm} \rvert \textnormal{Edct, Hrpw, Sex} \\
								\textnormal{Age} &\ci \textnormal{Occp} \rvert \textnormal{Edct, Sex} \\
								\textnormal{Age} &\ci \textnormal{Sex} \\
								\textnormal{Hrpw} &\ci \textnormal{Occp} \rvert \textnormal{Edct, Sex} \\
							\end{split}
						\end{equation*}
					\end{minipage}
					};
			\end{scope}
		\end{tikzpicture}
		\caption{\todo[inline]{Show a full example of testing using this model}}
\end{figure}

@@

% \begin{algorithm}
% 	\caption{Expert Simulation}
% 	\While{True}{
% 	   $ e \gets \textnormal{Effects}(G) > \textnormal{THRESHOLD} $\;
% 	   $ e \gets e - \textnormal{blacklist} $\;
% 	   \If {$ e = 0 $}{
% 		$ G \gets G - e $ \;
% 		$ \textnormal{blacklist} \gets \textnormal{blacklist} \cup e $\;
% 	   } \;
% 	   \If{$ \textnormal{len}(e) = 0$}{
% 		   $ \textnormal{return}(G) $\;
% 	   }
% 	   $ X, Y \gets \max_{X, Y} e $\;
% 	   $ dir \gets Expert(X, Y, \alpha) $\;
% 	   $ G \gets G \cup dir $\;
% 	}
% 
% \end{algorithm}

@@

\subsection{Results}
\begin{figure}
	\begin{subfigure}{0.5\textwidth}
		\includegraphics{../code/plots/shd_ribbon.pdf}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\includegraphics{../code/plots/sid_ribbon.pdf}
	\end{subfigure}
\end{figure}

@@

\bibliography{references}
\end{document}
